---
title: "Simulations for Factorial Design arranged as RCBD"
author: "Vinicius C. Garnica and Denis A. Shah"
date: "2/8/2023"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen=1, digits=2)
```


```{r Library,warning=FALSE,message=FALSE}
library(tidyverse)
library(multcomp)
library(agricolae)
library(emmeans)
library(lme4)
library(furrr) 
library(data.table)
library(DescTools)
theme_set(theme_bw())
```



```{r Algorithm and Post hoc test formulas}
{
get_MSD=function(value,letter){
  require(data.table)
  letter=letter[order(value,decreasing = T)]
  value=value[order(value,decreasing = T)]
  n=abs(apply(combn(value,2), 2, diff))
  l=combn(letter,2)
  dt=as.data.table(t(rbind(n,l)))
  dt$n=as.numeric(dt$n)
  dt$range=sequence((length(value)-1):1)+1
  dt=dt[order(dt$n),]
  dt$inter = !sapply(gsub(" ", "", paste(dt$V2, dt$V3)), function(x) any(str_count(x, letters)>1))
  dt[dt==""]=NA
  dt=na.omit(dt)
  if(all(dt$V2==dt$V3) || length(rle(dt$inter)$lengths)==1){
    data=as.data.table(rbind(rep(NA,ncol(dt)),rep(NA,ncol(dt))))
    colnames(data) = colnames(dt)
    return(data)}
  else{
    msd_1=dt[inter==FALSE, .SD[which.max(n)], by=inter] 
    msd_2=dt[inter==TRUE, .SD[which.min(n)], by=inter]
    msd=rbind(msd_1,msd_2)}
  return(msd) 
}


Fisher_MSE= function(msd,rep,alpha,df){
  mse=0.5*unique(rep)*(msd/qt(1-unique(alpha)/2,unique(df)))^2
  return(mse)}
Tukey_MSE= function(msd,rep,alpha,df,n_factor){
  mse=unique(rep)*(msd/qtukey(1-unique(alpha),unique(n_factor),unique(df)))^2
  return(mse)
}
Bonferroni_MSE= function(msd,rep,alpha,df,n_factor){
  k=choose(unique(n_factor),2)
  mse=0.5*unique(rep)*(msd/qt(1-((unique(alpha)/2)/k),unique(df)))^2
  return(mse)
}
Sidak_MSE= function(msd,rep,alpha,df,n_factor){
  k=choose(unique(n_factor),2)
  mse=0.5*unique(rep)*(msd/qt(1-(1-(unique(alpha))/2)^(1/k),unique(df)))^2
  return(mse)
}
Scheffe_MSE= function(msd,rep,alpha,df,n_factor){
  mse=(unique(rep)*msd^2)/(2*(unique(n_factor)-1)*qf(1-unique(alpha),unique(n_factor)-1,unique(df)))
  return(mse)
}

# ---------------------------------------------------------------

Fisher_MSE_ab= function(msd,rep,alpha,df,n_other_factor){
  mse=0.5*unique(rep)*unique(n_other_factor)*(msd/qt(1-alpha/2,df))^2
  return(mse)
}
Tukey_MSE_ab= function(msd,rep,alpha,df,n_factor,n_other_factor){
  mse=unique(n_other_factor)*unique(rep)*(msd/qtukey(1-unique(alpha),unique(n_factor),unique(df)))^2
  return(mse)
}
Bonferroni_MSE_ab= function(msd,rep,alpha,df,n_factor,n_other_factor){
  k=choose(unique(n_factor),2)
  mse=0.5*unique(n_other_factor)*unique(rep)*(msd/qt(1-((unique(alpha)/2)/k),unique(df)))^2
  return(mse)
}
Sidak_MSE_ab= function(msd,rep,alpha,df,n_factor,n_other_factor){
  k=choose(unique(n_factor),2)
  mse=0.5*unique(n_other_factor)*unique(rep)*(msd/qt(1-(1-(unique(alpha))/2)^(1/k),unique(df)))^2
  return(mse)
}
Scheffe_MSE_ab= function(msd,rep,alpha,df,n_factor,n_other_factor){
  mse=(unique(rep)*unique(n_other_factor)*msd^2)/(2*(unique(n_factor)-1)*qf(1-unique(alpha),unique(n_factor)-1,unique(df)))
  return(mse)
}
}
```

```{r Helper-functions}
# Two-way interaction helper function:
two.way.fxn = function(x, y,int_mu, int_sd, seed) {
  # Interaction effect (when the i-th level of A and the j-th level of B are combined):
  # Args:
  #  x = the number of levels of factor 1
  #  y = the number of levels of factor 2
  #  seed = seed for RNG
  # Returns:
  # a x by y matrix of sampled numbers from a standard normal distribution N(0, 1)
  # (of course, can also change the mean and sd input to rnorm, or set them as function args)
  #
  # set seed for reproducibility:
  set.seed(seed)
  m = matrix(rnorm(n = x*y,mean = int_mu , sd = int_sd), nrow = x)
  return(m)
}

```

# Model

<!-- Factorial treatments in an RCB design -->
$y{ijk} = \mu + \alpha_i + \beta_j + (\alpha \beta)_{ij} + \rho_k + \epsilon_{ijk}$


$\mu$ = overall mean
$\alpha_i$ = effect of the i-th level of A
$\beta_j$ = effect of the j-th level of B
$(\alpha \beta)_{ij}$ = interaction effect of the i-th level of A and the j-th level of B
$\rho_i$ = effect due to the i-th replicate (of the incomplete blocks)

Assumptions:
$\epsilon$ are i.i.d. $N(0, \sigma^2_\epsilon$


```{r RCBD-factorial}
RCBD.factorial.sim = function(num_A = NULL, num_B = NULL, num_blk = NULL, mu = NULL, e.sd = NULL, .seed) {
  # Simulate data for factorial treatments in an RCB design
  # Args:
  #   num_A = number of levels of factor A
  #   num_B = number of levels of factor B
  #   num_blk = number of blocks
  #   mu = overall mean
  #   e.sd = residual error standard deviation. Residuals ~Norm(0, e.sd^2)
  #   .seed = seed for random number generation
  # Returns:
  #  a data frame of the simulated data

  set.seed(.seed)
  # Effects due to the levels of A
  A.mu = rnorm(n = num_A, mean = 3, sd = 2.5)
  # Effects due to the levels of B
  B.mu = rnorm(n = num_B, mean = 3, sd = 2.5)
  # Effects due to the num_blk blocks
  Blk.mu = rnorm(n = num_blk, mean = 0.5, sd = 1.2)
  
  # Now generate the matrix of the A*B interaction effects:
  AB.mu = two.way.fxn(x = num_A, y = num_B,int_mu = 1, int_sd = 1.5,seed = .seed) # interaction effects
  
  # The simulated data:
  df =
    expand_grid(Blk = 1:num_blk, A = 1:num_A, B = 1:num_B) %>%
    mutate(y = pmap_dbl(list(A, B, Blk), function(.A, .B, .Blk) {mu + A.mu[.A] + B.mu[.B] + AB.mu[.A, .B] + Blk.mu[.Blk] + rnorm(n = 1, mean = 0, sd = e.sd)})) %>%
    # fewer mistakes will occur if we use words to encode the levels of a factor:
    mutate(A = str_c("A", A), B = str_c("B", B), Blk = str_c("Blk", Blk)) %>%
    mutate(across(Blk:B, factor))
  
  return(df)
  }


# Set a "plan" for how the code should run.
plan(multisession, workers = 5)

# simulate 10000 trials

trials = 10000

df = future_map(1:trials, function(x) RCBD.factorial.sim(num_A = sample(4:7,1),
                                                         num_B = sample(4:7,1),
                                                         num_blk = sample(3:5,1),
                                                         mu = rgamma(1,shape = 60.2,rate = 1), # trial average varying as a gamma
                                                         e.sd = 8,
                                                         .seed = x), .options = furrr_options(seed = 123))



plan(sequential)


```


```{r Model fit}

model = vector("list")
sig.A = vector("list")
sig.I = vector("list")

for(i in 1:length(df)){
  contrasts(df[[i]]$A) <- contr.sum
  contrasts(df[[i]]$B) <- contr.sum
  contrasts(df[[i]]$Blk) <- contr.sum
  model[[i]] = aov(y ~ Blk + A + B + A:B, df[[i]]) # fit the model
  sig.I[[i]]=summary(model[[i]])[1][[1]][[5]][[4]]<=0.05 # check for p-value on Interaction
  sig.A[[i]]=summary(model[[i]])[1][[1]][[5]][[2]]<=0.05 & sig.I[[i]]==FALSE# check for p-value on A 
 }

# Extract only significant trials. Of course the number of trials with significant results will vary based on the parameters used in the simulation.


sum(sig.I==TRUE)/trials
sum(sig.A==TRUE)/trials

## data frames

        df_I=df[unlist(sig.I)]
        model_int=model[unlist(sig.I)]
        pick=sample(length(df_I), 1000)
        df_I=df_I[pick]
        model_int=model_int[pick]
        
        
        df_A=df[unlist(sig.A)]
        model_A=model[unlist(sig.A)]
        pick=sample(length(df_A), 1000)
        df_A=df_A[pick]
        model_A=model_A[pick]

```


```{r Calculate degrees of freedom}
# Interaction


for(i in 1:length(df_I)){
  df_I[[i]]$n.Blks = nlevels(df_I[[i]]$Blk) # obtain the number of Blks per trial
  df_I[[i]]$n.trt_A = nlevels(df_I[[i]]$A) # obtain the number of trt A per trial
  df_I[[i]]$n.trt_B = nlevels(df_I[[i]]$B) # obtain the number of trt B per trial
  df_I[[i]]$degrees_freedom = (df_I[[i]]$n.trt_A)*(df_I[[i]]$n.trt_B)*(df_I[[i]]$n.Blks-1) #calculate the degrees of freedom
}
```

# Variances for interaction A x B


## Fisher LSD

```{r,warning=FALSE,message=FALSE,fig.height=3,fig.width=3}
means=vector("list")
msd=vector("list")

for(i in 1:length(df_I)){
   means[[i]]=as.data.table(cld(emmeans(model_int[[i]], ~A*B),adjust='none',Letters=letters))
   msd[[i]]=get_MSD(means[[i]]$emmean,means[[i]]$.group)
   df_I[[i]]$mse_model= summary(model_int[[i]])[1][[1]][[3]][[5]]
   df_I[[i]]$mse_algorithm= Fisher_MSE(mean(msd[[i]]$n,na.rm=TRUE),df_I[[i]]$n.Blks,0.05,df_I[[i]]$degrees_freedom)
}


dt_fisher_ab= unique(data.frame(
                          mse_model=unlist(lapply(df_I, `[`, 9),use.names = F),
                          mse_algorithm=unlist(lapply(df_I, `[`, 10),use.names = F))) %>% na.omit()


lin=CCC(dt_fisher_ab$mse_model,dt_fisher_ab$mse_algorithm, ci = "z-transform", conf.level = 0.95)
lin$rho.c
lin$s.shift
lin$l.shift
lin$C.b
cor.test(dt_fisher_ab$mse_model,dt_fisher_ab$mse_algorithm)

```


## Tukey-Kramer HSD 

```{r,warning=FALSE,message=FALSE,fig.height=3,fig.width=3}
means=vector("list")
msd=vector("list")

for(i in 1:length(df_I)){
   means[[i]]=as.data.table(cld(emmeans(model_int[[i]],~A*B),Letters=letters))
   msd[[i]]=get_MSD(means[[i]]$emmean,means[[i]]$.group)
   df_I[[i]]$mse_algorithm=Tukey_MSE(mean(msd[[i]]$n,na.rm=TRUE),df_I[[i]]$n.Blks,0.05,df_I[[i]]$degrees_freedom,(df_I[[i]]$n.trt_A*df_I[[i]]$n.trt_B))
}

dt_tukey_ab= unique(data.frame(
                          mse_model=unlist(lapply(df_I, `[`, 9),use.names = F),
                          mse_algorithm=unlist(lapply(df_I, `[`, 10),use.names = F))) %>% na.omit()

lin=CCC(dt_tukey_ab$mse_model,dt_tukey_ab$mse_algorithm, ci = "z-transform", conf.level = 0.95)
lin$rho.c
lin$s.shift
lin$l.shift
lin$C.b
cor.test(dt_tukey_ab$mse_model,dt_tukey_ab$mse_algorithm)
```

## Bonferroni

```{r,warning=FALSE,message=FALSE,fig.height=3,fig.width=3}
means=vector("list")
msd=vector("list")

for(i in 1:length(df_I)){
   means[[i]]=as.data.table(cld(emmeans(model_int[[i]],~A*B),adjust='bonferroni',Letters=letters))
   msd[[i]]=get_MSD(means[[i]]$emmean,means[[i]]$.group)
   df_I[[i]]$mse_algorithm=Bonferroni_MSE(mean(msd[[i]]$n,na.rm=TRUE),df_I[[i]]$n.Blks,0.05,df_I[[i]]$degrees_freedom,(df_I[[i]]$n.trt_A*df_I[[i]]$n.trt_B))
}

dt_bon_ab=unique(data.frame(
                          mse_model=unlist(lapply(df_I, `[`, 9),use.names = F),
                          mse_algorithm=unlist(lapply(df_I, `[`, 10),use.names = F))) %>% na.omit()



lin=CCC(dt_bon_ab$mse_model,dt_bon_ab$mse_algorithm, ci = "z-transform", conf.level = 0.95)
lin$rho.c
lin$s.shift
lin$l.shift
lin$C.b
cor.test(dt_bon_ab$mse_model,dt_bon_ab$mse_algorithm)

```

## Dunn-Sidak 

```{r,warning=FALSE,message=FALSE,fig.height=3,fig.width=3}
means=vector("list")
msd=vector("list")

for(i in 1:length(df_I)){
   means[[i]]=as.data.table(cld(emmeans(model_int[[i]],~A*B),adjust='sidak',Letters=letters))
   msd[[i]]=get_MSD(means[[i]]$emmean,means[[i]]$.group)
   df_I[[i]]$mse_algorithm= Sidak_MSE(mean(msd[[i]]$n,na.rm=TRUE),df_I[[i]]$n.Blks,0.05,df_I[[i]]$degrees_freedom,(df_I[[i]]$n.trt_A*df_I[[i]]$n.trt_B))
}

dt_sid_ab= unique(data.frame(
                          mse_model=unlist(lapply(df_I, `[`, 9),use.names = F),
                          mse_algorithm=unlist(lapply(df_I, `[`, 10),use.names = F))) %>% na.omit()



lin=CCC(dt_sid_ab$mse_model,dt_sid_ab$mse_algorithm, ci = "z-transform", conf.level = 0.95)
lin$rho.c
lin$s.shift
lin$l.shift
lin$C.b
cor.test(dt_sid_ab$mse_model,dt_sid_ab$mse_algorithm)
```


## Scheffe

```{r,warning=FALSE,message=FALSE,fig.height=3,fig.width=3}
means=vector("list")
msd=vector("list")

for(i in 1:length(df_I)){
   means[[i]]=as.data.table(cld(emmeans(model_int[[i]],~A*B),adjust='scheffe',Letters=letters))
   msd[[i]]=get_MSD(means[[i]]$emmean,means[[i]]$.group)
   df_I[[i]]$mse_algorithm= Scheffe_MSE(mean(msd[[i]]$n,na.rm=TRUE),df_I[[i]]$n.Blks,0.05,df_I[[i]]$degrees_freedom,(df_I[[i]]$n.trt_A*df_I[[i]]$n.trt_B))
}


dt_sch_ab=unique(data.frame(
                          mse_model=unlist(lapply(df_I, `[`, 9),use.names = F),
                          mse_algorithm=unlist(lapply(df_I, `[`, 10),use.names = F))) %>% na.omit()


lin=CCC(dt_sch_ab$mse_model,dt_sch_ab$mse_algorithm, ci = "z-transform", conf.level = 0.95)
lin$rho.c
lin$s.shift
lin$l.shift
lin$C.b

cor.test(dt_sch_ab$mse_model,dt_sch_ab$mse_algorithm)
```


```{r}

dt_bon_ab$method="Bonferroni"
dt_sid_ab$method="Sidak"
dt_tukey_ab$method="Tukey"
dt_fisher_ab$method="Fisher"
dt_sch_ab$method="Scheffe"


dt=rbind(dt_bon_ab,dt_fisher_ab,dt_sch_ab,dt_sid_ab,dt_tukey_ab)
dt$design="factorial_rcbd_ab"
save(dt, file = "factorial_rcbd_ab.RData")


```

```{r}

dt %>% 
  ggplot(aes(x=mse_model,y=mse_algorithm))+
  geom_point(alpha=0.1,size=0.8) +
  labs(x="Actual MSE",y="MSE FindR estimate")+
  geom_abline(intercept = 0, slope = 1, size = 0.3,linetype = "dashed") +
  geom_smooth(method='lm', formula= y~x, se = FALSE)+
  facet_wrap(~method)+
  theme_bw() +
  coord_fixed(ratio = 1)+
  theme(strip.text.y = element_text(size = 4),
        strip.text.x = element_text(size = 4),
        axis.text=element_text(size=5))

```

```{r}
rm(dt_bon_ab)
rm(dt_sid_ab)
rm(dt_tukey_ab)
rm(dt_fisher_ab)
rm(dt_sch_ab)
rm(dt)

```




# Variances for main factor A

```{r}
# Main effect

for(i in 1:length(df_A)){
  df_A[[i]]$n.Blks = nlevels(df_A[[i]]$Blk) # obtain the number of Blks per trial
  df_A[[i]]$n.trt_A = nlevels(df_A[[i]]$A)# obtain the number of trt A per trial
  df_A[[i]]$n.trt_B = nlevels(df_A[[i]]$B) # obtain the number of trt B per trial
  df_A[[i]]$degrees_freedom = (df_A[[i]]$n.trt_A-1)*(df_A[[i]]$n.trt_B)*(df_A[[i]]$n.Blks-1) #calculate the degrees of freedom
}

```



## Fisher LSD


```{r,warning=FALSE,message=FALSE,fig.height=3,fig.width=3}
means=vector("list")
msd=vector("list")

for(i in 1:length(df_A)){
  means[[i]]=as.data.table(cld(emmeans(model_A[[i]], ~A),adjust='none',Letters=letters))
  msd[[i]]=get_MSD(means[[i]]$emmean,means[[i]]$.group)
  df_A[[i]]$mse_model= summary(model_A[[i]])[1][[1]][[3]][[5]]
  df_A[[i]]$mse_algorithm= Fisher_MSE_ab(mean(msd[[i]]$n,na.rm=TRUE),df_A[[i]]$n.Blks,0.05,df_A[[i]]$degrees_freedom,df_A[[i]]$n.trt_B)
}

dt_fisher_ab= unique(data.frame(
                          mse_model=unlist(lapply(df_A, `[`,9),use.names = F),
                          mse_algorithm=unlist(lapply(df_A, `[`, 10),use.names = F))) %>% na.omit()


lin=CCC(dt_fisher_ab$mse_model,dt_fisher_ab$mse_algorithm, ci = "z-transform", conf.level = 0.95)
lin$rho.c
lin$s.shift
lin$l.shift
lin$C.b

cor.test(dt_fisher_ab$mse_model,dt_fisher_ab$mse_algorithm)

```

## Tukey-Kramer HSD 

```{r,warning=FALSE,message=FALSE,fig.height=3,fig.width=3}
means=vector("list")
msd=vector("list")

for(i in 1:length(df_A)){
  means[[i]]=as.data.table(cld(emmeans(model_A[[i]],~A,adjust='tukey'),Letters=letters))
  msd[[i]]=get_MSD(means[[i]]$emmean,means[[i]]$.group)
  df_A[[i]]$mse_algorithm=Tukey_MSE_ab(mean(msd[[i]]$n,na.rm=TRUE),df_A[[i]]$n.Blks,0.05,df_A[[i]]$degrees_freedom,df_A[[i]]$n.trt_A,df_A[[i]]$n.trt_B)
}


dt_tukey_ab= unique(data.frame(
                          mse_model=unlist(lapply(df_A, `[`,9),use.names = F),
                          mse_algorithm=unlist(lapply(df_A, `[`, 10),use.names = F))) %>% na.omit()

lin=CCC(dt_tukey_ab$mse_model,dt_tukey_ab$mse_algorithm, ci = "z-transform", conf.level = 0.95)
lin$rho.c
lin$s.shift
lin$l.shift
lin$C.b

cor.test(dt_tukey_ab$mse_model,dt_tukey_ab$mse_algorithm)

```

## Bonferroni

```{r,warning=FALSE,message=FALSE,fig.height=3,fig.width=3}
means=vector("list")
msd=vector("list")

for(i in 1:length(df_A)){
  means[[i]]=as.data.table(cld(emmeans(model_A[[i]],~A),adjust='bonferroni',Letters=letters))
  msd[[i]]=get_MSD(means[[i]]$emmean,means[[i]]$.group)
  df_A[[i]]$mse_algorithm=Bonferroni_MSE_ab(mean(msd[[i]]$n,na.rm=TRUE),df_A[[i]]$n.Blks,0.05,df_A[[i]]$degrees_freedom,df_A[[i]]$n.trt_A,df_A[[i]]$n.trt_B)
}


dt_bon_ab= unique(data.frame(
                          mse_model=unlist(lapply(df_A, `[`,9),use.names = F),
                          mse_algorithm=unlist(lapply(df_A, `[`, 10),use.names = F))) %>% na.omit()

lin=CCC(dt_bon_ab$mse_model,dt_bon_ab$mse_algorithm, ci = "z-transform", conf.level = 0.95)
lin$rho.c
lin$s.shift
lin$l.shift
lin$C.b
cor.test(dt_bon_ab$mse_model,dt_bon_ab$mse_algorithm)

```

## Dunn-Sidak 

```{r,warning=FALSE,message=FALSE,fig.height=3,fig.width=3}
means=vector("list")
msd=vector("list")

for(i in 1:length(df_A)){
  means[[i]]=as.data.table(cld(emmeans(model_A[[i]],~A),adjust='sidak',Letters=letters))
  msd[[i]]=get_MSD(means[[i]]$emmean,means[[i]]$.group)
  df_A[[i]]$mse_algorithm=Sidak_MSE_ab(mean(msd[[i]]$n,na.rm=TRUE),df_A[[i]]$n.Blks,0.05,df_A[[i]]$degrees_freedom,df_A[[i]]$n.trt_A,df_A[[i]]$n.trt_B)
}


dt_sid_ab=unique(data.frame(
                          mse_model=unlist(lapply(df_A, `[`,9),use.names = F),
                          mse_algorithm=unlist(lapply(df_A, `[`, 10),use.names = F))) %>% na.omit()

lin=CCC(dt_sid_ab$mse_model,dt_sid_ab$mse_algorithm, ci = "z-transform", conf.level = 0.95)
lin$rho.c
lin$s.shift
lin$l.shift
lin$C.b
cor.test(dt_sid_ab$mse_model,dt_sid_ab$mse_algorithm)
```


## Scheffe

```{r,warning=FALSE,message=FALSE,fig.height=3,fig.width=3}
means=vector("list")
msd=vector("list")

for(i in 1:length(df_A)){
  means[[i]]=as.data.table(cld(emmeans(model_A[[i]],~A),adjust='scheffe',Letters=letters))
  msd[[i]]=get_MSD(means[[i]]$emmean,means[[i]]$.group)
  df_A[[i]]$mse_algorithm=Scheffe_MSE_ab(mean(msd[[i]]$n,na.rm=TRUE),df_A[[i]]$n.Blks,0.05,df_A[[i]]$degrees_freedom,df_A[[i]]$n.trt_A,df_A[[i]]$n.trt_B)
}

dt_sch_ab= unique(data.frame(
                          mse_model=unlist(lapply(df_A, `[`,9),use.names = F),
                          mse_algorithm=unlist(lapply(df_A, `[`, 10),use.names = F))) %>% na.omit()

lin=CCC(dt_sch_ab$mse_model,dt_sch_ab$mse_algorithm, ci = "z-transform", conf.level = 0.95)
lin$rho.c
lin$s.shift
lin$l.shift
lin$C.b
cor.test(dt_sch_ab$mse_model,dt_sch_ab$mse_algorithm)

```

```{r}

dt_bon_ab$method="Bonferroni"
dt_sid_ab$method="Sidak"
dt_tukey_ab$method="Tukey"
dt_fisher_ab$method="Fisher"
dt_sch_ab$method="Scheffe"


dt=rbind(dt_bon_ab,dt_fisher_ab,dt_sch_ab,dt_sid_ab,dt_tukey_ab)
dt$design="factorial_rcbd_a"
save(dt, file = "factorial_rcbd_a.RData")


```

```{r}

dt %>% 
  ggplot(aes(x=mse_model,y=mse_algorithm))+
  geom_point(alpha=0.1,size=0.8) +
  labs(x="Actual MSE",y="MSE FindR estimate")+
  geom_abline(intercept = 0, slope = 1, size = 0.3,linetype = "dashed") +
  geom_smooth(method='lm', formula= y~x, se = FALSE)+
  facet_wrap(~method)+
  theme_bw() +
  coord_fixed(ratio = 1)+
  theme(strip.text.y = element_text(size = 4),
        strip.text.x = element_text(size = 4),
        axis.text=element_text(size=5))

```

```{r Session info}
sessionInfo()
```